Research Paper: Proposal

### 2014-11-01 BME 560/proposal.tex
Final

\documentclass{article}
\usepackage{tgbonum}
\usepackage{graphicx}
\title{Research Paper: Proposal}
\author{Rahul Krishna \\ 200020531}
\date{\today}
\begin{document}
	\maketitle
	\section{Introduction}
	\begin{list}{--}
	\item In the reseach paper for this term I plan on exploring Intensity Modulated Radiotherapy. 
	\item At the time the refered survey paper was complied, the technique was relatively new and implemented in only a few imaging centers around the world. In my survey, I'll include the results of some comparative studies and clinical trials that have been performed to show the efficacy of IMRT.
	\item The two types of tomotherapy-- linear and helical tomotheraphy. 
	\item Dose distribution
	\item Challenges in tomotherapy 
	\end{list}\end{document}

>>>>

\documentclass[12pt]{article}
\usepackage{tgbonum}
\usepackage{graphicx}
%\usepackage{natbib}
\linespread{1}
\setlength{\parindent}{0em}
\setlength{\parskip}{0.735em}
\usepackage{fullpage}
\title{Research Paper: Proposal}
\author{Rahul Krishna \\ 200020531}
\usepackage{cite}
%\usepackage{hyperref}
\date{\today}
\begin{document}
\maketitle
\section* {Introduction}
My survey paper for this will be based on two comprehensive papers on intensity modulated tomotherapy Refs. \cite{IMRT2001}, \cite{Mackie2006}. In the paper, I will provide a comprehensive description of the following --- the history and early development that led to this form of radiotherapy, Serial and Helical Tomotherapy, the recent advances in the field, and the clinical implementation.

In addition, I will present a comparision between the two types of tomotherapy namely, Serial Tomotherapy and Helical Tomotherapy. It is my understanding that the technique is still relatively new and at the time Ref. \cite{IMRT2001} was complied, the technique was implemented in only a few imaging centers around the world. And therefore, in my survey, I will include the results of some comparative studies and clinical trials that have been performed since to show the efficacy of tomotherapy, both serial and helical.

Moreover, the results of dose distribution will be provided and I will  contrast it with other radiotherapy methods. I will also dedicate a section in the paper to discuss the challenges in tomotherapy and what is being done to overcome it.
\bibliography{proposal}{}
\bibliographystyle{ieeetr}
\end{document}
